Optimizing Abstract Abstract Machines

### 2012-11-15 paper/paper.tex
Use PDF for figures.  Better make.

\begin{figure}[t]
\begin{center}
\includegraphics[width=3.2in]{church-relative-space.ps}
\includegraphics[width=3.2in]{church-relative-speed.ps}
\includegraphics[width=3.2in]{church-relative-time.ps}
\vspace{-1.5em}
\end{center}
\caption{Factor improvements over the baseline analyzer for the
  \Church{} benchmark in terms of peak memory usage, the rate of state
  transitions, and total analysis time. (Bigger is better.) Each point
  is marked with the section that introduces the optimization.}
\label{fig:churchtime}
\end{figure}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=6.5in]{all-relative-memory.ps}

@@

  \vspace{1em}
  \includegraphics[width=6.5in]{all-relative-speed.ps}

@@

  \vspace{1em}
  \includegraphics[width=6.5in]{all-relative-time.ps}

>>>>

\begin{figure}[t]
\begin{center}
\includegraphics[width=3.2in]{church-relative-space}
\includegraphics[width=3.2in]{church-relative-speed}
\includegraphics[width=3.2in]{church-relative-time}
\vspace{-1.5em}
\end{center}
\caption{Factor improvements over the baseline analyzer for the
  \Church{} benchmark in terms of peak memory usage, the rate of state
  transitions, and total analysis time. (Bigger is better.) Each point
  is marked with the section that introduces the optimization.}
\label{fig:churchtime}
\end{figure}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=6.5in]{all-relative-space}

@@

  \vspace{1em}
  \includegraphics[width=6.5in]{all-relative-speed}

@@

  \vspace{1em}
  \includegraphics[width=6.5in]{all-relative-time}
